### 2025-05-27 conteudo/results/students.tex
add work 26-05

BLABLABLA

>>>>

We asked for the teaching assistant and the student that used the ArKanjo to answer a survey with some 
question related to the tool experience, such as installation, documentation, facility of use, new ideas
to improve the tool, etc. Appendix \ref{app:survey} has the complete survey with the answers.

Related to the tool installation, the teaching assistant nor the students faced issues installing on the
Debian distributions, although the teaching assistant attempted to install in the Arch Linux distribution and
failed to install on this linux distribution.  About the tool documentation, the teaching assistant pointed errors in 
the documentation that worsed his experience. The student asked for more examples 
and tutorials on using the tool, in text or video formats.

On the ArKanjo tool preprocessing step, the student reported problems of disk space usage and crash errors,
which we knew that could happen as the tool iterates and can save information about every pair of functions in
a codebase, as we did not implemented any mechanism to control the memory usage. The teaching assistant reported 
to only be able to execute the preprocessor with the \textit{gensim} similarity method, and the \textit{diff}
method kepted running for hours without finishing. This was a unexpected behaviour to us, as the \textit{gensim}
is a text similarity method while the \textit{diff} method is a simple counter of common lines with a operation system
default command. The teaching assistant report corroborate the \textit{gensim} efficiency.

Related to the functionalites of the tool, both the student assistant and the student 
reported a missing of a mechanism to save the tool results on a separated file instead of the terminal output.
The tool by default outputted with colors as show in the section \ref{subsec:func}, which complicates to redirect
the terminal output to a file.

We asked the overall impression of the tool and if met their expectations and to give a score from one 
to five to installation, documentation, preprocessing, and functionalites. 
Both the teaching assistant and the student gave a score of at least 4 to each mentioned point,
thought that the tool fulfill their expectations and have a overall good experience.

Finally, the teaching assistant the the student reported features ideas to the tool that may be interesting, which 
is as follow:

\begin{itemize}

\item Enable the possibility to have several codebases preprocessor artifacts and to select one of them.

\item Addition of different methods to find duplication.

\item Addition of more filters to search duplication, such as , find duplicates with
more than 90\% of similarity and more than 20 lines repeated.

\item Addition of options to highligh and filter duplications that happen on same file or directory.

\item Addition of support to save the tool output in files without manual preprocessing of the colored output.

\end{itemize}

With the survey feedback, we understood the the users had a good experience and found value in the ArKanjo tool,
and provided critical points that could be improved in the tool. The most critical issues reported had been fixed,
such as documentation errors and support for multiple linux distribution and different operation system. 
The less critical issues became a open point that can be addressed in future works.
